### 2024-03-04 sections/1stratified.tex

The spaces that this work will be set in will very often be stratified spaces. Thus, we first need to define what we mean by this concept. There are multiple definitions of stratified spaces in the literature, all of which have their advantages and disadvantages. For our purposes, we will follow the account of \cite{aft_localstrut}. A compatible source is also \cite[sec.A.5]{lurie_ha}. The majority of the work on factorization homology has so far been elaborated using this particular set of definitions, and similarly the stratified spaces used in the literature on factorization algebras are usually subsumed too. Here we will only recap the results that will be of use to us. Further details are, of course, discussed in \cite{aft_localstrut}, where one can find a great explanation of the definitions that are needed, and detailed proofs of the theorems that can be proven.

>>>>

The spaces that this work will be set in will very often be stratified spaces. Thus, we first need to define what we mean by this concept. There are multiple definitions of stratified spaces in the literature, all of which have their advantages and disadvantages. For our purposes, we will follow the account of \cite{aft_localstrut}. A compatible source is also \cite[sec.A.5]{lurie_ha}. The majority of the work on factorization homology has so far been elaborated using this particular set of definitions, and similarly the stratified spaces used in the literature on factorization algebras are usually subsumed too. Here we will only recap the definitions, results and examples that will be of use to us. Further details are, of course, discussed in the original \cite{aft_localstrut}, where one can find great explanations of the definitions that are needed, and detailed proofs of the theorems that can be proven.
